---
title: "BMI 882 Homework 1"
author: "Li Ge"
date: "2/27/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The homework requirement is [here](https://kbroman.org/BMI882/hw1.html).

## Reproduce Figure 1b

First, I downloaded the [source materials](https://bioinformatics.mdanderson.org/Supplements/ReproRsch-All/), specifically, [Everything (177 MB)](https://bioinformatics.mdanderson.org/Supplements/ReproRsch-All/everything.zip). Unzip it, go to the subfolder **/RNowebSource**, and then the **examiningDoxorubicinInDetail.Rnw** file for the details of section 2 - Case study 1: Doxorubicin. Then straight copy and paste the minimal code required to recreate figure 1b. The subtitles are just the r section names in their original **examiningDoxorubicinInDetail.Rnw** file. I do have to copy and paste the **/RawData/PottiNatMed** subfolder to my working directory to load the data to just run the original code. 

### loadGenes

```{r, echo = T, results = 'hide'}
doxorubicinGenes <- 
  read.table(file.path("RawData","PottiNatMed",
                       "GeneListsNov07","Adria(final).txt"),
             sep="\t",header=TRUE)
dim(doxorubicinGenes)
doxorubicinGenes[1:3,]
doxorubicinGenes <- as.character(doxorubicinGenes[,"Probe.Set.ID"])
doxorubicinGenes[1:3]

```

### loadDoxo07
```{r, echo = T, results = 'hide'}
tempDoxorubicin07Header1 <- 
  read.table(file.path("RawData","PottiNatMed","Adria_ALL.txt"), sep="\t",
             nrows=1, header=FALSE)
tempDoxorubicin07Header1 <- as.vector(t(tempDoxorubicin07Header1));

tempDoxorubicin07Header2 <- 
  read.table(file.path("RawData","PottiNatMed","Adria_ALL.txt"), sep="\t",
             skip=1, nrows=1, header=FALSE)
tempDoxorubicin07Header2 <- as.vector(t(tempDoxorubicin07Header2));

tempDoxorubicin07Header1[1:25]
tempDoxorubicin07Header2[1:25]

table(tempDoxorubicin07Header1)
table(tempDoxorubicin07Header2)
```

### buildDoxo07Info

```{r, echo = T, results = 'hide'}
tempSampleNames <- 
  c(paste("Training", c(1:22), sep=""), 
    paste("Test", c(1:122), sep=""))

tempGroup <- c(rep("Training", 22), rep("Test", 122))
tempStatus <- tempDoxorubicin07Header2
tempStatus[tempStatus == "Sens"] <- "Sensitive"
tempStatus[tempStatus == "NR"]   <- "Resistant"
tempStatus[tempStatus == "Resp"] <- "Sensitive"

doxorubicin07Info <- 
  data.frame(sampleGroup = tempGroup,
             status      = tempStatus,
             row.names   = tempSampleNames)

doxorubicin07Info[c(1:2,22:25),]

#rm(doxorubicin07Header1, doxorubicin07Header2, tempGroup, tempStatus)
rm(list=ls(pattern="^temp"))
```

### loadDoxo07Numbers
```{r, echo = T, results = 'hide'}
doxorubicin07Numbers <- 
  read.table(file.path("RawData","PottiNatMed","Adria_ALL.txt"), sep="\t",
             skip=2, header=FALSE)

colnames(doxorubicin07Numbers) <- rownames(doxorubicin07Info)

doxorubicin07Numbers[1:4,c(1:2,22:25)]
```

### getDoxoCors
```{r, echo = T, results = 'hide'}
doxorubicin07Cors <- cor(doxorubicin07Numbers)
sum(doxorubicin07Cors > 0.9999)
sum(diag(doxorubicin07Cors) > 0.9999)
```

### plotDoxoHighCors
```{r}
doxorubicin07HighCors <- (doxorubicin07Cors > 0.9999)

same07Status <- matrix(rep(doxorubicin07Info[,"status"],144),144,144)
same07Status <- (same07Status == t(same07Status))

temp07Ties <- which(doxorubicin07HighCors & same07Status, arr.ind=TRUE)
temp07Ties <- temp07Ties[temp07Ties[,1] != temp07Ties[,2],]
temp07BadTies <- which(doxorubicin07HighCors & (!same07Status), arr.ind=TRUE)

plot(1:144, 1:144, pch=".", cex=3,
     xlim=c(0.5,144.5), ylim=c(0.5,144.5), 
     xaxs="i", yaxs="i",
     xlab="Column in Adria_ALL.txt",
     ylab="Column in Adria_ALL.txt",
     main="Identical Columns in Adria_ALL.txt",
     )
points(temp07Ties[,1],temp07Ties[,2],pch=21,bg="white",lwd=1)
points(temp07BadTies[,1],temp07BadTies[,2],pch=24,bg="red",lwd=2)
abline(h=22.5, v=22.5)

abline(v=32, lty="dashed")
```


